### 2010-11-20 docs/tex/review.tex
Artificial Life.

\section{Artificial Life}

>>>>

\section{Artificial Life}
As Artificial Intelligence is the field of computer science where scientists take concepts from psychology and implement into computer science. In contrast to that in Artificial Life scientist take concepts from Biology specially Evolutionary Biology and genetics and implement into computer science.

In defining Artificial Life Christopher G. Langton states the following,

\begin{quote}
`` `Art' + `Life' = Artificial Life: Life made by Man rather than by Nature. Our technological capabilities have brought us to the point where we are on the verge of creating `living' artifacts. The field of Artificial Life is devoted to studying the scientific, technological, artistic, philosophical, and social implications of such an accomplishment."
\end{quote}

\section{History}

%\paragraph{Jon Von Neumann}

%\paragraph{Tierra}

%\paragraph{Avida}

The field of Artificial Life (AL) has been described by Taylor as a tool for biological inquiry \cite{taylor1993}. While providing a brief survey over different AL models he talks about \textbf{wetware systems} which work at the molecular level, the \textbf{software systems} which work at the cellular level and the \textbf{hardware systems} which works at the organism level.
